\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. We have identified two areas where typical NMT models differ significantly from other deep-learning models that impact on their inference speed. Firstly, NMT models usually contains a large number of output classes, corresponding to the output vocabulary. Secondly, rather than a single label, the output from machine translation models is a sequence of class labels that makes up the words or sub-words in the target sentence. The sentence lengths are unpredictable, leading to inefficiencies during batch processing. We provide solutions for each of these issues which can increase batched inference speed by up to 57\% on modern GPUs without affecting model quality.

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Fused Kernel}{vector $p$, bias vector $b$}

>>>>

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. We have identified two areas where typical NMT models differ significantly from other deep-learning models that impact on their inference speed. Firstly, NMT models usually contains a large number of output classes, corresponding to the output vocabulary. Secondly, rather than a single label, the output from machine translation models is a sequence of class labels that makes up the words or sub-words in the target sentence. Target sentence lengths are unpredictable, leading to inefficiencies during batch processing. We provide solutions for each of these issues which together increase batched inference speed by up to 57\% on modern GPUs without affecting model quality.

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Fused-Kernel}{vector $p$, bias vector $b$}
